---
title: "Problems and solutions about Adv-R"
author: "Carolyn-Yu"
date: "2020/3/19"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

The version of R I'm using is R version 3.6.3

## When I open the project(Adv-r.Rproj) using Rstudio:  
Error in loadNamespace(name) : there is no package called ‘rmarkdown’

So I install the package bookdown by
```{r eval=FALSE}
install.packages("rmarkdown")
```

## And then I install the “bookdown” package to compile the book:
```{r eval=FALSE}
install.packages("bookdown")
bookdown::render_book("index.Rmd",output_format="bookdown::pdf_book")
```

## During the building process I meet some problems, I list my problems and solutions below:

* The problem 1:   

Q: The error that there is no package called “…”

S: During the building process, I install some packages, such as dplyr, desc, sessioninfo, lobstr, ggplot2, devtools, sloop, DBI, RSQLite, zealot, profvis, bench, tidyr
  
  
* The problem 2:    

Q: Quitting from lines 223-235 (Introduction.Rmd) 
Error in cat(paste0(contributors$desc, collapse = ", ")) :

S: I add encoding="UTF-8" in line 224 of introduction.rmd to fix it.
```{r eval=FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, encoding = "UTF-8")
```
  
  
* The problem 3:    

Q: When I install the package “emo” with install.package:
Warning in install.packages :
  package ‘emo’ is not available (for R version 3.6.3)

S: So I install the package ”devtools”, and then install the package “emo” from Hadley's github.com by
```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("hadley/emo")
```
  
  
* The problem 4:    

Q: Quitting from lines 209-221 (Big-picture.Rmd) 
erro: The dbplyr package is required to communicate with database backends

S: The solution:
```{r eval=FALSE}
install.packages("dbplyr")
```
  
  
* The problem 5:    

Q: Quitting from lines 233-234 (Perf-measure.Rmd) 
erro: `ggbeeswarm` must be installed to use `type = "beeswarm"` option

S: The solution:
```{r eval=FALSE}
install.packages("ggbeeswarm")
```
  
  
* The problem 6:    

Q: ATeX failed to compile _main.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips.

S: I find some relevant information on the Internet, and then I choose to use MiKTeX instead of TinyTex
  
  
* The problem 7:    

Q: LaTeX Error: Font inconsola & andale mono not found

S:I download the “inconsola” and “andale mono” from Internet and then install them
  
  
* The problem 8:   

Q: LaTeX Error: File `xeCJK.sty' not found

S: I install the package “xecjk” from MikTex Console
  
   

